% Lecture 02: If Planck Prosecuted Cagliostro for Gacha Fraud
% Timeline Prequel - Lecture 00
\documentclass[12pt]{article}
\usepackage{amsmath,amssymb,physics,bm}
\usepackage{graphicx}
\usepackage[dvipsnames]{xcolor}
\usepackage{tcolorbox}
\usepackage[colorlinks=true,
            linkcolor=MidnightBlue,
            urlcolor=RoyalBlue,
            citecolor=OliveGreen]{hyperref}

\title{Lecture 02 (a.k.a. Lecture 00): \\ If Planck Prosecuted Cagliostro for Gacha Fraud}
\author{Written by Junhu Park}
\date{Lecture 02 in Release, Lecture 00 in Timeline \\ April 17, 2025}

\begin{document}
\maketitle

\section*{Act 1. The Prosecution Opens}

\textbf{Scene:} The Alchemical Court of Arcadia. Lady Cagliostro stands accused of manipulating the probability mechanics of a gacha system to induce excessive downloadable content purchases. Max Planck\footnote{See \cite{planckWikipedia} for biographical background on Max Planck.} stands as the prosecutor; Werner Heisenberg\footnote{See \cite{heisenbergWikipedia} for Heisenberg’s contributions to quantum mechanics and uncertainty.} serves as defense counsel. Paul Dirac observes silently from the gallery.

\begin{tcolorbox}[title=Planck (Prosecutor):]
You claimed that continuous purchases yield continuous rewards. Yet the actual rewards were quantized. This deception mirrors the downfall of classical blackbody radiation theory\footnote{See Planck’s resolution of the ultraviolet catastrophe via quantized energy emission \cite{planck1901law}.}!
\end{tcolorbox}

\begin{tcolorbox}[title=Cagliostro (Defendant):]
Oh my~ Alchemy is about beauty and profit, isn’t it? Isn’t it only natural to show off the prettiest probabilities\footnote{See \cite{CagliostroWikipedia} for Cagliostro’s flair for aesthetic and economic alchemy.}?
\end{tcolorbox}

\textbf{Planck presents the disparity between classical expectations and quantum hypotheses:}
\[
E_n = n\hbar \omega, \quad n \in \mathbb{N} \footnote{The quantization of energy levels was first introduced by Planck to explain blackbody radiation \cite{planck1901law}.}
\]

\begin{tcolorbox}[title=Planck:]
Just as I abandoned the continuous model of blackbody radiation and introduced quantization\footnote{The introduction of the energy quantum marked the birth of quantum theory \cite{griffiths2018introduction,sakurai2020modern}.}, your gacha system masquerades as continuous—yet it's fundamentally discrete!
\end{tcolorbox}

\section*{Act 2. The Uncertainty of Gacha}

\begin{tcolorbox}[title=Heisenberg (Defense Counsel):]
Have you ever observed the probability of a gacha you did not roll?
\end{tcolorbox}

\begin{tcolorbox}[title=Cagliostro:]
Of course not! Only the beautiful pulls are worth looking at~\footnote{A tongue-in-cheek reflection of observer bias in gacha culture. See also \cite{GachaWikipedia}.}
\end{tcolorbox}

\textbf{Heisenberg invokes the Uncertainty Principle—recontextualized for consumer systems:}
\[
\Delta G \cdot \Delta P \geq \frac{\hbar}{2} \footnote{Adapted metaphorically from Heisenberg’s uncertainty principle, where $\Delta x \cdot \Delta p \geq \hbar/2$ expresses the intrinsic limits of simultaneous measurement \cite{heisenberg1927anschaulichen, griffiths2018introduction}.}
\]
Here, \( \Delta G \) represents the uncertainty in gacha outcomes, and \( \Delta P \) the uncertainty in purchase intent.

\begin{tcolorbox}[title=Heisenberg:]
To fix the sentence is to blur the crime. To confirm guilt is to render the sentence uncertain. The same is true in gacha: unobserved probabilities do not exist\footnote{Philosophically akin to the Copenhagen interpretation, which asserts that quantum properties have no definite value until measured \cite{neumann1955mathematical}.}.
\end{tcolorbox}

\section*{Act 3. Quantum of Purchase}

\begin{tcolorbox}[title=Planck:]
If purchases are continuous, shouldn’t the outcomes be so as well? That was our naive belief about blackbody radiation too\footnote{In classical physics, blackbody emission was expected to be continuous across all frequencies—an expectation shattered by the ultraviolet catastrophe \cite{planck1901law,griffiths2018introduction}.}.
\end{tcolorbox}

\begin{tcolorbox}[title=Cagliostro:]
But the world isn’t that simple, darling~! Games deliver value in quantum packets: merch drops, character unlocks... \textbf{Even doujinshi are quantized goods, are they not?}\footnote{This metaphor reflects the quantization of energy levels—discrete and indivisible—as first formalized by Planck \cite{planck1901law}.}
\end{tcolorbox}

\textbf{Planck mutters in an aside.}

\begin{tcolorbox}[title=Planck (aside):]
Once again... it seems the quantum hypothesis explains reality better than I dared expect\footnote{Planck’s reluctant acceptance of energy quantization marked a turning point in modern physics \cite{sakurai2020modern}.}.
\end{tcolorbox}

\section*{Act 4. The Time-Reversed Trial}

\textbf{Scene:} Just before the verdict, Dirac rises quietly from the gallery, his voice almost a whisper against the ticking of the courtroom clock.

\begin{tcolorbox}[title=Dirac (aside):]
Time does not flow in one direction—like the wavefunction, it contains all paths\footnote{This reflects the time-symmetric interpretations of quantum theory and Feynman–Stueckelberg's treatment of antiparticles as particles moving backward in time \cite{dirac1981principles,carroll2004introduction}.}. If trials exist across the timeline, then remembering a past one means another has vanished. As though a hole has appeared in the Dirac sea\footnote{Dirac’s sea of negative-energy states proposed the existence of positrons as ``holes'' in a filled vacuum \cite{dirac1981principles}.}.
\end{tcolorbox}
    
\begin{tcolorbox}[title=Dirac:]
Unbought goods do not exist. But... when a hole forms, reality begins to leak\footnote{An allegorical nod to quantum field theory, where vacua are not empty, and absences are just as real as presences \cite{zurek2002decoherence}.}.
\end{tcolorbox}

\section*{Epilogue: Lecture 00}

This trial shall be recorded as a prelude to the upcoming “Lecture 01,” marking the beginning of a quantum entanglement between payments, probabilities, and the flow of time.

\textbf{Final Scene:} As all characters exit, the in-game statistics screen displays:

\[
\sum_{n=1}^{\infty} P_n = 1, \quad \text{where } P_n = 0 \text{ if not purchased.} \footnote{A meta-quantum analogy: all possible states exist, but unobserved (or unbought) states are effectively zeroed by decoherence \cite{zurek2002decoherence}.}
\]

\bibliographystyle{plain}
\bibliography{refs}


\end{document}
